---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
comma <- function(x) {
  paste0(paste(x[-length(x)], collapse = ", "), ", and ", x[length(x)])
}
```

# tidyverse

[![Travis-CI Build Status](https://travis-ci.org/hadley/tidyverse.svg?branch=master)](https://travis-ci.org/hadley/tidyverse)

The goal of tidyverse is to make it easy to install and load multiple tidyverse packages in a single command.

## Installation

You can install tidyverse from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("hadley/tidyverse")
```

This will also install tidyverse packages `r comma(tidyverse:::tidyv_packages(FALSE))`.

## Usage

Use `library(tidyverse)` to automatically load the tidyverse packages you are likely to use in almost every analysis: `r comma(tidyverse:::load)`. You also get a condensed summary of conflicts with other packages you have loaded:

```{r example}
library(tidyverse)
```

You can see conflicts created later with `tidyverse_conflicts()`:

```{r conflicts, message = FALSE}
library(MASS)
tidyverse_conflicts()
```

And you can check that all tidyverse pacakges are up-to-date with `tidyverse_update()`:

```{r update, eval = FALSE}
tidyverse_update()
#> The following packages are out of date:
#>  * broom (0.4.0 -> 0.4.1)
#>  * DBI   (0.4.1 -> 0.5)
#>  * psych (1.5.8 -> 1.6.6)
#>  * Rcpp  (0.12.6 -> 0.12.7)
#> Update now?
#> 
#> 1: Yes
#> 2: No
```
